% Who do I want to thank for my project
It is hard to believe I've spent nearly a decade at Missouri S\&T. I am eternally grateful to everyone at this university who helped me along the way.  Bruce McMillin got me started down this long path of research when he hired me to work with David Cape and has provided me with so many opportunities. I have had so many wonderful experiences with everyone I've worked with in the Computer Science department.

Special thanks to Ali Hurson, Wei Jiang,  Sahra Sedigh Sarvestani, and Sriram Chellappan for their service on my Ph.D. committee. I'm very grateful to every instructor I've had at S\&T who has inspired me to explore and learn. Thanks to Dawn Davis, Christina Barton, and Rhonda
Grayson for their years of administrative support. Thanks to all my lab mates: Li Feng, Thomas Roth, Gerry Howser, and everyone else along the way for making our lab such a great place to work.

My research was supported by the two excellent programs:  the Future Renewable Electric Energy Delivery and Management Center, a National Science Foundation-supported Engineering Research Center under grant NSF EEC-081212, and the United States Department of Education GAANN program.

Special thanks to my family: Sue, Kent, Laura, and everyone else who encouraged me and supported me through this long journey. I also want to give thanks to all of my friends for their support: Emily, Drew, Doug, Tony, Michaela, Liz, Robert, Remington, Dwight and everyone else at KMNR; you've made this long stay at S\&T a lot  more comfortable. I love you all.
