
\subsection{Worst Case Results}

In the worst case, supply processes and demand processes are not intermixed at each switch: only supply processes are at switch A, and only demand processes are at switch B.
The placement of processes is the worst case because it involves the highest number of messages crossing the congested link.
No migration can occur without messages crossing the congested link.
As a result, in the worst case scenarios, hard \ac{ECN} messages are triggered at a much lower level of traffic than in the average case scenarios.
This is expected: in soft \ac{ECN} mode, the majority of traffic comes from the load balancing algorithm and in the worst case, the load balancing algorithm can only perform migrations while using the congested link.
The parameters necessary to protect the system in the average case make \acp{ECN} in worst case overly proactive when attempting to protect the system. 
A summary of test scenarios for the worst case is presented in \ref{tab:scenarios-worst}.

\begin{table}
\centering
\caption{Summary of Scenarios Run}
\begin{tabular}{| c | c | c | c |}
    \hline
    Test & Traffic & Notifications & Attempted Migrations \\ \hline
    G & 4Mbps & None &  \\ \hline
    H & 4Mbps & Soft &  \\ \hline
    I & 5.1Mbps & Soft & \\ \hline
    J & 5.1Mbps & All &  \\ \hline
\end{tabular}
\label{tab:scenarios-worst}
\end{table}

Figure X shows the number of lost migrations for each scenario.
Because all migrations must be completed with the congested link, there is a greater number of failed migrations and the number of migrations attempted is reduced because of the congestion (Scenario G).
The queue size for Scenario G is presented in Figure Y.
Enabling soft ECN mode (Scenario H), as before, prevents failed migrations.
Scenario G's queue is presented in figure Z.

The hard ECN message is triggered earlier in the worst case, due to the increased dependence on the congested link.
Figure ZA shows the queue size for Scenario I, a scenario that should trigger hard ECN mode.
In Scenario I, uncontrolled group division occur and migrations are lost.
By enabling notifications (Scenario J) those situations are mitigated.
