In a ditributed system information cannot be instantenously spread throughout the system.
A process can only make localized observations.
In this work, we attempt to model what a process will observe as a result of omission failure.
Therefore, it is important that observations that a process makes hold to the Markov property.
In the original algorithm, there are several portions that, when projected to the leader's observation, do not meet the Markov property.
The following sections state the portions of the algorithm where the observation of the leader process does not yield the probability of next transition.

Leader selection is performed apriori-- only process 0 may become a group coordinator.
In this work, the consequence of this is that only process 0 may become the leader of a multiprocess group.
This simplification was applied because the configuration of the system with a larger number of processes depended on the configuration of the other processes.
A process

The changes added a third message to completing an election -- a ready acknowledge message.
This message is sent by a member after receiving the ready message from the coordinator.
This allows the coordinator to be certain of the member's status before the next round.
Without the ready acknowledgement, the member may not receive the ready message and the coordinator will observe the member is a part of the group.
As a consequence, the probability that a member remains in a group in the first round after an election has a different probability than each subsequent round.

By adding the extra message, the observation of the coordinator of the state, must be the state of the member of the group.
The sequence presented in figure _____ is not possible and as a consequence, the probability a member remains in a group in the first round after an election is a fixed value.

Members cannot leave a group without the leader's permission.
Members do not suspect the coordinator has failed, only the coordinator may suspect the members.
For the purpose of starting an election, an Are You There message and it's negative response are considered equivalent to a Are You Coordinator message and a postive response.
On receipt of the negative response, the member will immediately recover and become a leader.

This change leads to a livelock situation in a crash failure, where the group's leader crashes and does not return and as a consequence the remaining members are trapped in a group without a leader.
For the purpose of this work, we have disregarded these live lock scenarios.
However, one should note that the livelock could be avoided if the member can detect that it has not received an "Are You Coordinator" message in a round.
When the process fails to receive the message, the coordinator must have also removed the member from their group since they could not have received a "Are You Coordinator" response message.


