%\begin{center}SECTION\end{center}

\chapter{CONCLUSIONS}

\section{CHARACTERIZATION OF TRANSPORT REGIME TRANSITIONS IN NON-CONSERVATIVE RANDOM MEDIA}

The purpose of the first portion of this dissertation was to characterize the effect of absorption and gain in ballistic, diffusive, and localized transport regimes. Particle and wave-based transport models were studied in one dimension (1D) and quasi-1D geometries. 

An investigation of the ratio of transmission to energy in the system, $T/{\cal E}$, was performed in 1D using theoretical and numerical methods~\cite{2010_Payne_TE}. %~(c.f.~Section \ref{sec:TE2009}). 
The numerical model uses the transfer matrix method~\cite{1981_MacKinnon_scaling} with self-embedding~\cite{1999_yamilov_selfembed} to simulate layers of dielectric material with random widths. Since diffusion cannot occur in 1D, the response of the parameter $T/{\cal E}$ in the regime of Anderson localization when gain is present was found. A decrease of $T/{\cal E}$ from the value given by the classical un-renormalized diffusion coefficient may be attributed to wave-interference localization effects. Although $T/{\cal E}$ does not diverge as the random lasing threshold is approached, there is a dependence on the position of the center of localization. This position dependence is closely related to the existance of necklace states~\cite{1987_Pendry}. 

To investigate the transition from diffusion to Anderson localization, the previous numerical model was extended to quasi-1D geometry. To guide our efforts we developed a phase space diagram with 15 different transport regimes~\cite{2010_Yamilov_Regimes}. A way of characterizing which regime a given system is in was clearly needed. In the process of using the numerical model in this geometry, we showed that evanescant channels do not need to be included in simulations of passive media~\cite{2010_Payne_closed}. The effect of evanescant channels is renormalize the transport mean free path while conforming to single parameter scaling. 

A parameter related to $T/{\cal E}$, the position dependent diffusion coefficient $D(z)$, was investigated for use in characterizing the multiple transport regimes in quasi-1D non-conservative random media~\cite{2010_Payne_PRL}. Our results indicate that $D(z)$ may serve as a useful criterion for the enumerated transport regimes. 

\section{ANALYSIS OF DETERMINISTIC APERIODIC STRUCTURES}



Although random media produces novel features, these systems lack easy reproducibility. For applications such as photonic integrated circuits we are interested in novel features unavailable to periodic media while maintaining reproducibility. Thus media correlated disorder is a natural avenue of pursuit. The numerical model used in this dissertation can simulate any arrangement of scatters, making it amenable to aperiodic media. %The same simulation tool used for random media was applied to aperiodic media. 

In the studies of deterministic aperiodic structures (DAS) we focused on the Thue-Morse pattern. This generation algorithm yeilds a singular continuous Fourier transform spectrum with self-similar features. We demonstrated the possibility of mapping the array of micro-cavities in the two dimensional (2D) Thue Morse DAS onto a periodic square lattice~\cite{2012_Payne_Mapping_2D_TM}. Such mapping allowed us to uniquely identify and enumerate the configurations of nearest and next-nearest neighbors. Thus the original aperiodic structure is reduced to the periodic structure with aperiodic arrangement of the limited set of pairings. 

Once this step was completed, we demonstrated the applicability of the tight binding approach in a deterministic aperiodic array of photonic micro-cavities. Under realistic conditions, we observed hybridization of the modes of individual micro-cavities into the eigenstates of the entire array. Our work adds the tight binding approach to the arsenal of theoretical tools for studying of 2D~Thue-Morse structures as well as for design and analysis of experiments.

The tight binding model allows us to investigate the size scaling of the density of the optical states in large arrays of optical micro-cavities; monitor the evolution of the spectra; and to study spatial properties of the eigenstates via e.g. the inverse participation ratio. The inverse participation ratio shows coexistence of localized and extended states in the same spectral regions. Some of the extended states have nearly constant intensity across the entire sample. This property makes the considered system extremely promising for practical applications in optical control of light propagation via e.g. wave-front shaping.
 


%\section{TEST OF BORDERS}

%Lorem ipsum dolor sit amet, consectetuer adipiscing elit. Ut purus elit, vestibulum ut, placerat ac, adipiscing vitae, felis. Curabitur dictum gravida mauris. Nam arcu libero, nonummy eget, consectetuer id, vulputate a, magna. Donec vehicula augue eu neque. Pellentesque habitant morbi tristique senectus et netus et malesuada fames ac turpis egestas. Mauris ut leo. Cras viverra metus rhoncus sem. Nulla et lectus vestibulum urna fringilla ultrices. Phasellus eu tellus sit amet tortor gravida placerat. Integer sapien est, iaculis in, pretium quis, viverra ac, nunc. Praesent eget sem vel leo ultrices bibendum. Aenean faucibus. Morbi dolor nulla, malesuada eu, pulvinar at, mollis ac, nulla. Curabitur auctor semper nulla. Donec varius orci eget risus. Duis nibh mi, congue eu, accumsan eleifend, sagittis quis, diam. Duis eget orci sit amet orci dignissim rutrum. Nam dui ligula, fringilla a, euismod sodales, sollicitudin vel, wisi. Morbi auctor lorem non justo. Nam lacus libero, pretium at, lobortis vitae, ultricies et, tellus. Donec aliquet, tortor sed accumsan bibendum, erat ligula aliquet magna, vitae ornare odio metus a mi. Morbi ac orci et nisl hendrerit mollis. Suspendisse ut massa. Cras nec ante. Pellentesque a nulla. Cum sociis natoque penatibus et magnis dis par turient montes, nascetur ridiculus mus. Aliquam tincidunt urna. Nulla ullamcorper vestibulum turpis. Pellentesque cursus luctus mauris. Lorem ipsum dolor sit amet, consectetuer adipiscing elit. Ut purus elit, vestibulum ut, placerat ac, adipiscing vitae, felis. Curabitur dictum gravida mauris. Nam arcu libero, nonummy eget, consectetuer id, vulputate a, magna. Donec vehicula augue eu neque. Pellentesque habitant morbi tristique senectus et netus et malesuada fames ac turpis egestas. Mauris ut leo. Cras viverra metus rhoncus sem. Nulla et lectus vestibulum urna fringilla ultrices. Phasellus eu tellus sit amet tortor gravida placerat. Integer sapien est, iaculis in, pretium quis, viverra ac, nunc. Praesent eget sem vel leo ultrices bibendum. Aenean faucibus. Morbi dolor nulla, malesuada eu, pulvinar at, mollis ac, nulla. Curabitur auctor semper nulla. Donec varius orci eget risus. Duis nibh mi, congue eu, accumsan eleifend, sagittis quis, diam. Duis eget orci sit amet orci dignissim rutrum. Nam dui ligula, fringilla a, euismod sodales, sollicitudin vel, wisi. Morbi auctor lorem non justo. Nam lacus libero, pretium at, lobortis vitae, ultricies et, tellus. Donec aliquet, tortor sed accumsan bibendum, erat ligula aliquet magna, vitae ornare odio metus a mi. Morbi ac orci et nisl hendrerit mollis. Suspendisse ut massa. Cras nec ante. Pellentesque a nulla. Cum sociis natoque penatibus et magnis dis par turient montes, nascetur ridiculus mus. Aliquam tincidunt urna. Nulla ullamcorper vestibulum turpis. Pellentesque cursus luctus mauris. Lorem ipsum dolor sit amet, consectetuer adipiscing elit. Ut purus elit, vestibulum ut, placerat ac, adipiscing vitae, felis. Curabitur dictum gravida mauris. Nam arcu libero, nonummy eget, consectetuer id, vulputate a, magna. Donec vehicula augue eu neque. Pellentesque habitant morbi tristique senectus et netus et malesuada fames ac turpis egestas. Mauris ut leo. Cras viverra metus rhoncus sem. Nulla et lectus vestibulum urna fringilla ultrices. Phasellus eu tellus sit amet tortor gravida placerat. Integer sapien est, iaculis in, pretium quis, viverra ac, nunc. Praesent eget sem vel leo ultrices bibendum. Aenean faucibus. Morbi dolor nulla, malesuada eu, pulvinar at, mollis ac, nulla. Curabitur auctor semper nulla. Donec varius orci eget risus. Duis nibh mi, congue eu, accumsan eleifend, sagittis quis, diam. Duis eget orci sit amet orci dignissim rutrum. Nam dui ligula, fringilla a, euismod sodales, sollicitudin vel, wisi. Morbi auctor lorem non justo. Nam lacus libero, pretium at, lobortis vitae, ultricies et, tellus. Donec aliquet, tortor sed accumsan bibendum, erat ligula aliquet magna, vitae ornare odio metus a mi. Morbi ac orci et nisl hendrerit mollis. Suspendisse ut massa. Cras nec ante. Pellentesque a nulla. Cum sociis natoque penatibus et magnis dis par turient montes, nascetur ridiculus mus. Aliquam tincidunt urna. Nulla ullamcorper vestibulum turpis. Pellentesque cursus luctus mauris. Lorem ipsum dolor sit amet, consectetuer adipiscing elit. Ut purus elit, vestibulum ut, placerat ac, adipiscing vitae, felis. Curabitur dictum gravida mauris. Nam arcu libero, nonummy eget, consectetuer id, vulputate a, magna. Donec vehicula augue eu neque. Pellentesque habitant morbi tristique senectus et netus et malesuada fames ac turpis egestas. Mauris ut leo. Cras viverra metus rhoncus sem. Nulla et lectus vestibulum urna fringilla ultrices. Phasellus eu tellus sit amet tortor gravida placerat. Integer sapien est, iaculis in, pretium quis, viverra ac, nunc. Praesent eget sem vel leo ultrices bibendum. Aenean faucibus. Morbi dolor nulla, malesuada eu, pulvinar at, mollis ac, nulla. Curabitur auctor semper nulla. Donec varius orci eget risus. Duis nibh mi, congue eu, accumsan eleifend, sagittis quis, diam. Duis eget orci sit amet orci dignissim rutrum. Nam dui ligula, fringilla a, euismod sodales, sollicitudin vel, wisi. Morbi auctor lorem non justo. Nam lacus libero, pretium at, lobortis vitae, ultricies et, tellus. Donec aliquet, tortor sed accumsan bibendum, erat ligula aliquet magna, vitae ornare odio metus a mi. Morbi ac orci et nisl hendrerit mollis. Suspendisse ut massa. Cras nec ante. Pellentesque a nulla. Cum sociis natoque penatibus et magnis dis par turient montes, nascetur ridiculus mus. Aliquam tincidunt urna. Nulla ullamcorper vestibulum turpis. Pellentesque cursus luctus mauris.

