%\specialhead{VITA}

Ben Payne was born on the planet Earth. As a Boy Scout he achieved the rank of Eagle Scout. From 2001 to 2008 he served as a crew chief on F-16s in the Air National Guard, earning an Associates degree in Aircraft Maintenance Technology from the Community College of the Air Force. At the University of Wisconsin-Madison he served as President and then Secretary of the UW-Madison Physics club from 2005 to 2007. He earned a Bachelors of Science from UW-Madison, majoring in both ``Applied Math, Engineering, and Physics'' and also in Physics. During this time he earned his private pilots license and skydiving license. While an undergraduate in Madison, Ben worked as a Network Administrator at the UW-Madison Office of the Registrar from 2002 to 2007. 

After he moved to Missouri, Ben was the founding employee at Micom LLC, again working as a Network Administrator. At Missouri University of Science and Technology he earned his Masters of Science in 2009 and Doctorate of Philosophy in May 2012. While there he greatly enjoyed his work as a research assistant to Dr. Alexey Yamilov for five years. He served as a teaching assistant in a unique role, helping to rewrite the undergraduate course content. In addition to publishing the papers presented in this dissertation, Ben presented his research at scientific meetings and participated in conferences discussing challenges in high performance computing. This was possible as a result of his securing competitive funding from the National Science Foundation. Ben earned multiple competition prizes for presentations given at the Missouri S\&T Physics department. He won awards from the Council of Graduate Students for ``Best Representative'' for two consecutive years. While in Rolla he served as the primary officer of the Missouri S\&T Skydiving club from~2007 to~2012. 
